|

### 2023-09-20 paper.Rmd
tighten language + maths + combine power figures to one

\noindent where $\boldsymbol{y}$, $\boldsymbol{x}$, $\boldsymbol{\varepsilon}$, $\boldsymbol{x}_{raw}$, $\boldsymbol{z}_{raw}$ are vectors of size $n$, $\boldsymbol{1}_n$ is a vector of ones of size $n$, $He_{j}(.)$ is the $j$th-order probabilist's Hermite polynomials, $\varepsilon \sim N(\boldsymbol{0}_n, \sigma^2\boldsymbol{I}_n)$, and $g(\boldsymbol{x}, k)$ is a scaling function to enforce the support of the random vector to be $[-k, k]^n$ defined as

@@

\noindent where $\displaystyle x_{min} = \min_{i\in \{1, ..., n\}} x_i$, $\displaystyle x_{max} = \max_{i\in \{1, ..., n\}} x_i$ and $x_i$ is the $i$-th entry of $\boldsymbol{x}$.

According to @abramowitz1964handbook, Hermite polynomials were initially defined by @de1820theorie, but named after @hermite1864nouveau because of the unrecognisable form of Laplace's work. The function `hermite` from the R package `mpoly` [@mpoly] is used to  simulate $\boldsymbol{z}_{raw}$ to generate Hermite polynomials.

@@

```{=tex}
\begin{equation} \label{eq:null-model}
\boldsymbol{y} = \beta_0\boldsymbol{1}_n + \beta_1 \boldsymbol{x} + \boldsymbol{u},
\end{equation}
```
\noindent where $\boldsymbol{u} \sim N(\boldsymbol{0}, \sigma^2\boldsymbol{I}_n)$. Since $z = O(x^j)$, for $j > 1$, $z$ is a higher order term left out of the null regression, which will lead to model misspecification.

@@

Visual patterns of non-linearity are simulated using four different orders of probabilist's Hermite polynomials ($j = 2, 3, 6, 18$). The values of $j$ were chosen so that distinct shapes of non-linearity were included in the residual plot. These include "U", "S", "M" and "triple-U" shape as shown in Figure \ref{fig:different-shape-of-herimite}. A greater value of $j$ will result in a curve with more turning points. It is expected that the "U" shape will be the easiest to detect, as the shape gets more complex it will be harder to perceive in a scatterplot, particularly when there is noise. Figure \ref{fig:different-sigma} shows the "U" shape for different amounts of noise ($\sigma$).

@@

\begin{align*} \label{eq:heter-model}
\boldsymbol{y} &= \boldsymbol{1}_n + \boldsymbol{x} + \boldsymbol{\varepsilon},\\
\boldsymbol{x} &= g(\boldsymbol{x}_{raw}, 1),\\
\boldsymbol{\varepsilon} &\sim N(\boldsymbol{0}_n, \boldsymbol{1}_n + (2 - |a|)(\boldsymbol{x} - a\boldsymbol{1}_n)^\top(\boldsymbol{x} - a\boldsymbol{1}_n) b \boldsymbol{I}_n), 
\end{align*}

@@

Fitted values are a function of the independent variables, and the distribution of the observed values affects the distribution of the fitted values. In the best case scenario the fitted values will have a uniform distribution, which means that there is even coverage of possible observed values across all of the predictors. This is not always present in the collected data. Sometimes the fitted values are discrete because one or more predictors were measured discretely. The distribution may be relatively Gaussian, reflecting a linear combination of many predictors, adhering to the Central Limit Theorem. It is also common to see a skewed distribution of fitted values if one or more of the predictors has a skewed distribution. This latter problem is usually corrected before modelling, using a variable transformation. Our simulation assess this by using four different distributions to represent fitted values, constructed by different sampling of the raw predictor $X_{raw}$:

@@

@@

Three different sample sizes were used in our experiment: $n = 50, 100, 300$. Figure \ref{fig:different-n} shows the non-linear "S" shape for different sample sizes. We expect signal strength to decline in the simulated data plots with smaller $n$. We chose 300 as the upper limit, because it is typically enough for structure to be visible in a scatterplot reliably. \textcolor{red}{Beyond 300, the scatterplot should probably be used with transparency or replaced with a density or binned plot. Scatterplots suffer from over-plotting.}

@@

\noindent where $\text{diag}(.)$ is the diagonal matrix constructed from the diagonal elements of a matrix,
$\boldsymbol{R} = \boldsymbol{I}_n - \boldsymbol{H}$ is the residual operator, $\boldsymbol{H} = \boldsymbol{X}(\boldsymbol{X}'\boldsymbol{X})^{-1}\boldsymbol{X}'$ is the hat matrix, $\boldsymbol{\mu}_z = \boldsymbol{R}\boldsymbol{Z}\boldsymbol{\beta}_z$ is the expected values of residuals where $\boldsymbol{Z}$ contain any higher order terms of $\boldsymbol{X}$ left out of the regression equation, $\boldsymbol{\beta}_z$ contains the corresponding coefficients, and $\sigma^2\boldsymbol{I}$ is the assumed covariance matrix of the error term when $H_0$ is true.

@@

To compute the effect size for each lineup we simulate a sufficient large number of samples from the same model, in each sample, the number of observations $n$ is fixed. We then compute the effect size for each sample and take the average as the final value. This ensures lineups constructed with the same experimental factors will share the same effect size.

@@

Data collection period III was primarily to obtain Rorschach lineup evaluations to estimate $\alpha$ from Equation \ref{eq:pvalue-beta-binomial}, and also to obtain additional evaluations of lineups made with uniform fitted value distribution to ensure consistency in the results. To construct a Rorschach lineup, the data is generated from a model with zero effect size, while the null data are generated using the same simulation method discussed in Section \ref{visual-test-procedure-based-on-lineups}. This procedure differs from that of the canonical Rorschach lineup, where all 20 plots are generated directly from the null model, so the method suggested in @vanderplas2021statistical for typical lineups containing a data plot is used to estimate $\alpha$. (The Appendix contains a sensitivity analysis on the effect of uncertainty in the estimation of $\alpha$.) The $3 \times 4 = 12$ treatment levels of the common factors, replicated three times results in 36 lineups. And 6 more evaluations on the 279 lineups with uniform fitted value distribution, results in at least $(36 \times 20 + 279 \times 3 \times 6) / (20-2) = 133$ participants needed.

@@

Data collection used a total of `r filter(vi_survey, !attention_check) %>% count(unique_lineup_id) %>% nrow()` lineups, and resulted in a total of `r nrow(filter(vi_survey, !attention_check))` evaluations from `r vi_survey %>% count(set, exp) %>% nrow()` participants. Roughly half corresponded to the two models, non-linearity and heteroskedasticiy, and the three collection periods had similar numbers of evaluations. Each participant received two of the `r vi_survey %>% filter(attention_check) %>% count(unique_lineup_id) %>% nrow()` attention check lineups which were used to filter results of participants who were clearly not making an honest effort (only 11 of `r vi_survey %>% count(set, exp) %>% nrow() + 11`). To estimate $\alpha$ for calculating statistical significance (see Section \ref{sig}) there were `r nrow(filter(vi_survey, null_lineup, !attention_check))` evaluations of `r vi_survey %>% filter(null_lineup, !attention_check) %>% count(unique_lineup_id) %>% nrow()` null lineups. Neither the attention checks nor null lineups were used in the subsequent analysis. The de-identified data, `vi_survey`, is made available in the R package, `visage`.

The data was collected on lineups constructed from four different fitted value distributions: uniform, normal, skewed and discrete. More data was collected on the uniform distribution (each evaluated by 11 participants) than the others (each evaluated by 5 participants). The analysis in Sections \ref{power-analysis}-\ref{hetero-analysis} uses only results from lineups generated with uniform fitted values, for a total `r nrow(filter(vi_survey, !attention_check, !null_lineup, x_dist == "uniform"))` lineup evaluations. This allows us to compare the conventional and visual test performance in an optimal scenario. Section \ref{effect-of-fitted-value-distributions} examines how the results may be affected if the fitted value distribution was different.

@@

Figures \ref{fig:polypower} and \ref{fig:heterpower} present the power curves of various tests plotted against the effect size in the residuals for non-linearity and heteroskedasticity respectively. In each case the power of visual test is calculated for multiple bootstrap samples leading to the many (orange) curves. The effect size was computed at a 5% significance level and plotted on a natural logarithmic scale. To facilitate visual calibration of effect size values with the corresponding diagnostic plots, a sequence of example residual plots with increasing effect sizes is provided at the bottom of these figures. These plots serve as a visual aid to help readers understand how different effect size values translate to changes in the diagnostic plots. The horizontal lines of dots at 0 and 1 represent the non-rejection or rejection decisions made by visual tests for each lineup.

@@

# Use area() to design layout
map(1:11, ~patchwork::area(21, .x, 22, .x)) %>%
  reduce(c) %>%
  c(patchwork::area(3, 1, 20, 11), .) %>%
  patchwork::wrap_plots(append(plist, list(p), after = 0), 
                        design = .)
```

@@

```{r heterpower, fig.height = 3, fig.width = 5, fig.cap = "Comparison of power between different tests for heteroskedasticity patterns (uniform fitted values only). Main plot shows the power curves, with dots indicating non-reject and reject in visual testing of lineups. The multiple lines for the visual test arise from estimating the power on many bootstrap samples. The row of scatterplots at the bottom are examples of residual plots corresponding to the specific effect sizes marked by vertical lines in the main plot.", dev = 'png', dpi = 450}

@@

# Use area() to design layout
map(1:11, ~patchwork::area(21, .x, 22, .x)) %>%
  reduce(c) %>%
  c(patchwork::area(3, 1, 20, 11), .) %>%
patchwork::wrap_plots(append(plist, list(p), after = 0), 
                      design = .)
```

Figure \ref{fig:polypower} compares the power for the different tests for non-linear structure in the residuals. The test with the uniformly higher power is the RESET test, one that specifically tests for non-linearity. Note that the BP and SW tests have much lower power, which is expected because they are not designed to detect non-linearity. The bootstrapped power curves for the visual test are effectively a shift right from that of the RESET test. This means that the RESET test will reject at a lower effect size (less structure) than the visual test, but otherwise the performance will be similar. In other words, the RESET test is more sensitive than the visual test. This is not necessarily a good feature for the purposes of diagnosing model defects: If we scan the residual plot examples at the bottom, we might argue that the non-linearity is not sufficiently problematic until an effect size of around 3 or 3.5. The RESET test would reject closer to an effect size of 2, but the visual test would reject closer 3.25, for a significance level of 0.05. The visual test matches the robustness of the model to (minor) violations of assumptions much better.

For the heteroskedasticity pattern, the power of BP test, designed for detecting heteroskedasticity, is uniformly higher than the other tests. The visual test power curve is a right shift. This shows a similar story to the power curves for non-linearity pattern: the conventional test is more sensitive than the visual test. From the example residual plots at the bottom we might argue that the heteroskedasticity becomes noticeably visible around an effect size of 3 or 3.5. However the BP test would reject at around effect size 2.5. Interestingly, the power curve for the SW test (for non-normality) is only slightly different to that of the visual test, suggesting that it performs reasonably for detecting heteroskedasticity, too. The power curve for the BP test suggests it is not useful for detecting heteroskedasticity, as expected.

@@

Surprisingly, the visual test rejects `r nr$n[1]` of the `r nr$n[1]+nr$n[2]` (`r round(nr$n[1]/(nr$n[1]+nr$n[2])*100, 0)`%) of lineups where the conventional test does not reject. Figure \ref{fig:heter-example} shows this lineup. The data plot in position seventeen displays a relatively strong heteroskedasticity pattern, and has a strong effect size ($log_e(E)=4.02$), which is reflected by the visual test $p\text{-value} = 0.026$. But the BP test $p\text{-value} = 0.056$, is slightly above the significance cutoff of $0.05$. This lineup was evaluated by 11 participants, it has experimental factors $a = 0$ ("butterfly" shape), $b = 64$ (large variance ratio), $n = 50$ (small sample size), and a uniform distribution for the fitted values. It may have been the small sample size and the presence of a few outliers that may have resulted in the lack of detection by the conventional test.

@@

Because the power curve of the visual tests are a shift to the right of the conventional test (Figures \ref{fig:polypower} and \ref{fig:heterpower}) we examined whether adjusting the significance level (to .001, .0001, .00001, ...) of the conventional test would generate similar decisions to that of the visual test. Interestingly, it doesn't: despite resulting less rejections, neither the RESET or BP tests come to complete agreement with the visual test (see Appendix).

@@

```{r heter-power-uniform-a, fig.height = 4, fig.cap = 'The effect of heteroskedasticity shape (parameter $a$) on the power of conventional and visual tests. The butterfly has higher power in both tests. Curiously, the visual test has slightly higher power for the "left-triangle" than the "right-triangle" shape, when it would be expected that they should be identical, which is observed in conventional testing.'}

>>>>

\noindent where $\boldsymbol{y}$, $\boldsymbol{x}$, $\boldsymbol{\varepsilon}$, $\boldsymbol{x}_{raw}$, $\boldsymbol{z}_{raw}$ are vectors of size $n$, $\boldsymbol{1}_n$ is a vector of ones of size $n$, $He_{j}(.)$ is the $j$th-order probabilist's Hermite polynomials [@hermite1864nouveau; originally by @de1820theorie], $\varepsilon \sim N(\boldsymbol{0}_n, \sigma^2\boldsymbol{I}_n)$, and $g(\boldsymbol{x}, k)$ is a scaling function to enforce the support of the random vector to be $[-k, k]^n$ defined as

@@

\noindent where $\displaystyle x_{min} = \min_{i\in \{1, ..., n\}} x_i$, $\displaystyle x_{max} = \max_{i\in \{1, ..., n\}} x_i$ and $x_i$ is the $i$-th entry of $\boldsymbol{x}$. The function `hermite` from the R package `mpoly` [@mpoly] is used to  simulate $\boldsymbol{z}_{raw}$ to generate Hermite polynomials.

<!--- ET: interesting history, but not pertinent to the story

According to @abramowitz1964handbook, Hermite polynomials were initially defined by @de1820theorie, but named after @hermite1864nouveau because of the unrecognisable form of Laplace's work. 
--->

@@

```{=tex}
\begin{equation} \label{eq:null-model}
\boldsymbol{y} = \beta_0\boldsymbol{1}_n + \beta_1 \boldsymbol{x} + \boldsymbol{u},
\end{equation}
```
\noindent where $\boldsymbol{u} \sim N(\boldsymbol{0}, \sigma^2\boldsymbol{I}_n)$. Here $\boldsymbol{z}$ is a higher order term of $\boldsymbol{x}$ and leaving it out in the null regression results in model misspecification.

<!--- ET: let's keep the language simpler.

Since $z = O(x^j)$, for $j > 1$, $z$ is a higher order term left out of the null regression, it leads to model misspecification. 
--->

@@

Visual patterns of non-linearity are simulated using four different orders of probabilist's Hermite polynomials ($j = 2, 3, 6, 18$). The values of $j$ were chosen so that distinct shapes of non-linearity were included in the residual plot. These include "U", "S", "M" and "triple-U" shape as shown in Figure \ref{fig:different-shape-of-herimite}. A greater value of $j$ will result in a curve with more turning points. It is expected that the "U" shape will be the easiest to detect, and as the shape gets more complex it will be harder to perceive in a scatterplot, particularly when there is noise. Figure \ref{fig:different-sigma} shows the "U" shape for different amounts of noise ($\sigma$).

@@

\begin{align*} \label{eq:heter-model}
\boldsymbol{y} &= \boldsymbol{1}_n + \boldsymbol{x} + \boldsymbol{\varepsilon},\\
\boldsymbol{x} &= g(\boldsymbol{x}_{raw}, 1),\\
\boldsymbol{\varepsilon} &\sim N(\boldsymbol{0}_n, \boldsymbol{1}_n + (2 - |a|)(\boldsymbol{x} - a\boldsymbol{1}_n)'(\boldsymbol{x} - a\boldsymbol{1}_n) b \boldsymbol{I}_n), 
\end{align*}

@@

Fitted values are a function of the independent variables, and the distribution of the observed values affects the distribution of the fitted values. In the best case scenario the fitted values will have a uniform distribution, which means that there is even coverage of possible observed values across all of the predictors. This is not always present in the collected data. Sometimes the fitted values are discrete because one or more predictors were measured discretely.  It is also common to see a skewed distribution of fitted values if one or more of the predictors has a skewed distribution. This latter problem is usually corrected before modelling, using a variable transformation. Our simulation assess this by using four different distributions to represent fitted values, constructed by different sampling of the raw predictor $X_{raw}$:

@@

<!--- ET: previous reference was "normal" but now Gaussian. This doesn't add to the story so I suggest just remove.

The distribution may be relatively Gaussian, reflecting a linear combination of many predictors, adhering to the Central Limit Theorem.

@@

Three different sample sizes were used in our experiment: $n = 50, 100, 300$. Figure \ref{fig:different-n} shows the non-linear "S" shape for different sample sizes. We expect signal strength to decline in the simulated data plots with smaller $n$. We chose 300 as the upper limit, because it is typically enough for structure to be visible in a scatterplot reliably. \textcolor{red}{Beyond 300, the scatterplot should probably be used with transparency or replaced with a density or binned plot as scatterplots suffer from over-plotting.}

@@

\noindent where $\text{diag}(.)$ is the diagonal matrix constructed from the diagonal elements of a matrix,
$\boldsymbol{R} = \boldsymbol{I}_n - \boldsymbol{H}$ is the residual operator, $\boldsymbol{H} = \boldsymbol{X}(\boldsymbol{X}'\boldsymbol{X})^{-1}\boldsymbol{X}'$ is the hat matrix, $\boldsymbol{\mu}_z = \boldsymbol{R}\boldsymbol{Z}\boldsymbol{\beta}_z$ is the expected values of residuals where $\boldsymbol{Z}$ contain any higher order terms of $\boldsymbol{X}$ left out of the regression equation, $\boldsymbol{\beta}_z$ contains the corresponding coefficients, and $\sigma^2\boldsymbol{I}_n$ is the assumed covariance matrix of the error term when $H_0$ is true.

@@

To compute the effect size for each lineup we simulate a sufficient large number of samples from the same model with the number of observations $n$ fixed for each sample. We then compute the effect size for each sample and take the average as the final value. This ensures lineups constructed with the same experimental factors will share the same effect size.

@@

Data collection period III was primarily to obtain Rorschach lineup evaluations to estimate $\alpha$ (see Section A.1 in the Appendix), and also to obtain additional evaluations of lineups made with uniform fitted value distribution to ensure consistency in the results. To construct a Rorschach lineup, the data is generated from a model with zero effect size, while the null data are generated using the same simulation method discussed in Section \ref{visual-test-procedure-based-on-lineups}. This procedure differs from that of the canonical Rorschach lineup, where all 20 plots are generated directly from the null model, so the method suggested in @vanderplas2021statistical for typical lineups containing a data plot is used to estimate $\alpha$. (The Appendix contains a sensitivity analysis on the effect of uncertainty in the estimation of $\alpha$.) The $3 \times 4 = 12$ treatment levels of the common factors, replicated three times results in 36 lineups. And 6 more evaluations on the 279 lineups with uniform fitted value distribution, results in at least $(36 \times 20 + 279 \times 3 \times 6) / (20-2) = 133$ participants needed.

@@

Data collection used a total of `r filter(vi_survey, !attention_check) %>% count(unique_lineup_id) %>% nrow()` lineups, and resulted in a total of `r nrow(filter(vi_survey, !attention_check))` evaluations from `r vi_survey %>% count(set, exp) %>% nrow()` participants. Roughly half corresponded to the two models, non-linearity and heteroskedasticiy, and the three collection periods had similar numbers of evaluations. Each participant received two of the `r vi_survey %>% filter(attention_check) %>% count(unique_lineup_id) %>% nrow()` attention check lineups which were used to filter results of participants who were clearly not making an honest effort (only 11 of `r vi_survey %>% count(set, exp) %>% nrow() + 11`). To estimate $\alpha$ for calculating statistical significance (see Section A.1 in the Appendix) there were `r nrow(filter(vi_survey, null_lineup, !attention_check))` evaluations of `r vi_survey %>% filter(null_lineup, !attention_check) %>% count(unique_lineup_id) %>% nrow()` null lineups. Neither the attention checks nor null lineups were used in the subsequent analysis. The de-identified data, `vi_survey`, is made available in the R package, `visage`.

The data was collected on lineups constructed from four different fitted value distributions: uniform, normal, skewed and discrete. More data was collected on the uniform distribution (each evaluated by 11 participants) than the others (each evaluated by 5 participants). The analysis in Sections \ref{power-analysis}--\ref{hetero-analysis} uses only results from lineups generated with uniform fitted values, for a total `r nrow(filter(vi_survey, !attention_check, !null_lineup, x_dist == "uniform"))` lineup evaluations. This allows us to compare the conventional and visual test performance in an optimal scenario. Section \ref{effect-of-fitted-value-distributions} examines how the results may be affected if the fitted value distribution was different.

@@

Figure \ref{fig:nonlinearheterpower} present the power curves of various tests plotted against the effect size in the residuals for non-linearity and heteroskedasticity. In each case the power of visual test is calculated for multiple bootstrap samples leading to the many (orange) curves. The effect size was computed at a 5% significance level and plotted on a natural logarithmic scale. To facilitate visual calibration of effect size values with the corresponding diagnostic plots, a sequence of example residual plots with increasing effect sizes is provided at the bottom of these figures. These plots serve as a visual aid to help readers understand how different effect size values translate to changes in the diagnostic plots. The horizontal lines of dots at 0 and 1 represent the non-rejection or rejection decisions made by visual tests for each lineup.

@@

# Use area() to design layout
A <- map(1:11, ~patchwork::area(21, .x, 22, .x)) %>%
  reduce(c) %>%
  c(patchwork::area(3, 1, 20, 11), .) %>%
  patchwork::wrap_plots(append(plist, list(p + labs(title = "(A) Non-linearity") + theme(plot.title = element_text(size = 10))), after = 0), 
                        design = .)
```

@@

```{r nonlinearheterpower, fig.cap = "Comparison of power between different tests for (A) non-linear and (B) heteroskedasticity patterns (uniform fitted values only). Main plot shows the power curves, with dots indicating non-reject and reject in visual testing of lineups. The multiple lines for the visual test arise from estimating the power on many bootstrap samples. The row of scatterplots at the bottom are examples of residual plots corresponding to the specific effect sizes marked by vertical lines in the main plot.", fig.height = 6.5, fig.width = 5, dev = 'png', dpi = 450}

@@

# Use area() to design layout
B <- map(1:11, ~patchwork::area(21, .x, 22, .x)) %>%
  reduce(c) %>%
  c(patchwork::area(3, 1, 20, 11), .) %>%
patchwork::wrap_plots(append(plist, list(p + labs(title = "(B) Heteroskedasticity") + theme(plot.title = element_text(size = 10))), after = 0), 
                      design = .)

A / B + patchwork::plot_layout(guides = "collect")
```

Figure \ref{fig:nonlinearheterpower}A compares the power for the different tests for non-linear structure in the residuals. The test with the uniformly higher power is the RESET test, one that specifically tests for non-linearity. Note that the BP and SW tests have much lower power, which is expected because they are not designed to detect non-linearity. The bootstrapped power curves for the visual test are effectively a shift right from that of the RESET test. This means that the RESET test will reject at a lower effect size (less structure) than the visual test, but otherwise the performance will be similar. In other words, the RESET test is more sensitive than the visual test. This is not necessarily a good feature for the purposes of diagnosing model defects: if we scan the residual plot examples at the bottom, we might argue that the non-linearity is not sufficiently problematic until an effect size of around 3 or 3.5. The RESET test would reject closer to an effect size of 2, but the visual test would reject closer to 3.25, for a significance level of 0.05. The visual test matches the robustness of the model to (minor) violations of assumptions much better.

For the heteroskedasticity pattern, the power of BP test, designed for detecting heteroskedasticity, is uniformly higher than the other tests. The visual test power curve shifts to the right. This shows a similar story to the power curves for non-linearity pattern: the conventional test is more sensitive than the visual test. From the example residual plots at the bottom we might argue that the heteroskedasticity becomes noticeably visible around an effect size of 3 or 3.5. However the BP test would reject at around effect size 2.5. Interestingly, the power curve for the SW test (for non-normality) is only slightly different to that of the visual test, suggesting that it performs reasonably for detecting heteroskedasticity, too. The power curve for the BP test suggests it is not useful for detecting heteroskedasticity, as expected.

@@

Surprisingly, the visual test rejects `r nr$n[1]` of the `r nr$n[1]+nr$n[2]` (`r round(nr$n[1]/(nr$n[1]+nr$n[2])*100, 0)`%) of lineups where the conventional test does not reject. Figure \ref{fig:heter-example} shows this lineup. The data plot in position seventeen displays a relatively strong heteroskedasticity pattern, and has a strong effect size ($\log_e(E)=4.02$), which is reflected by the visual test $p\text{-value} = 0.026$. But the BP test $p\text{-value} = 0.056$, is slightly above the significance cutoff of $0.05$. This lineup was evaluated by 11 participants, it has experimental factors $a = 0$ ("butterfly" shape), $b = 64$ (large variance ratio), $n = 50$ (small sample size), and a uniform distribution for the fitted values. It may have been the small sample size and the presence of a few outliers that may have resulted in the lack of detection by the conventional test.

@@

Because the power curve of the visual tests are a shift to the right of the conventional test (Figure \ref{fig:nonlinearheterpower}) we examined whether adjusting the significance level (to .001, .0001, .00001, ...) of the conventional test would generate similar decisions to that of the visual test. Interestingly, it doesn't: despite resulting in less rejections, neither the RESET or BP tests come to complete agreement with the visual test (see Appendix).

@@

```{r heter-power-uniform-a, fig.height = 4, fig.cap = 'The effect of heteroskedasticity shape (parameter $a$) on the power of conventional and visual tests. The butterfly has higher power in both tests. Curiously, the visual test has a slightly higher power for the "left-triangle" than the "right-triangle" shape, when it would be expected that they should be similar, which is observed in conventional testing.'}
